Hemispheric Lateralization in ICH

### 2023-05-20 code/dataAnalysis/02analysis.qmd
Update 02analysis.qmd

---
title: "Hemispheric Lateralization in ICH"
subtitle: "Analysis"
author: "Nikhil Patel"
project:
  type: default
format:
  html:
    code-fold: true
    code-tools: true
    toc: true
    html-math-method: katex
    css: "styles.css"
    fig-width: 12
---

```{r setup and data import}
#| output: false

library(tidyverse)
# library(gt) # Fancy tables
library(tableone)
library(data.table)
library(haven) # Importing SAS Files
library(janitor)
library(lubridate)
library(readxl)
library(Hmisc)
library(stringr)
library(qs)
library(glue)
library(scales) # Nicer labeling functions
library(ggmosaic) # Mosaic plots with ggplot
library(ggplot2)
library(ggpattern) # Pattern fills in ggplot
library(patchwork) # Combine plots nicely
library(systemfonts) ## use custom fonts (need to be installed on your OS)
library(scico) ## scico color palettes(http://www.fabiocrameri.ch/colourmaps.php) in R
library(ggtext) ## add improved text rendering to ggplot2
library(ggforce) ## add missing functionality to ggplot2
library(ggdist) ## add uncertainity visualizations to ggplot2
library(viridis)

@@

@@

Comparing outcomes between left and right hemisphere location overall. There does not appear to be a big difference.

```{r}

mrsCounts <- d |>
  filter(!is.na(mrs90)) |>
  group_by(ichLaterality, mrs90) |>
  tally(name = "patients") |>
  group_by(ichLaterality) |>
  mutate(percentPatients = patients / sum(patients)) |>
  ungroup() |>
  mutate(percentPatientsLabel = percent(percentPatients, accuracy = 1))

theme_set(theme_minimal(base_size = 20, base_family = "Figtree"))

ggplot(
  data = mrsCounts,
  aes(x = ichLaterality, y = percentPatients, fill = forcats::fct_rev(mrs90))
) +
  geom_bar(stat = "identity", position = "fill", width = 0.5) +
  geom_text(aes(label = patients),
    position = position_stack(vjust = 0.5),
    color = "white",
    size = 5,
    family = "FigTree"
  ) +
  coord_flip() +
  scale_y_continuous(
    name = NULL,
    labels = scales::percent_format(accuracy = 1),
    breaks = c(seq(0, 1, 0.2))
  ) +
  scale_x_discrete(name = NULL) +
  scale_fill_manual(values = myColors, breaks = c(0, 1, 2, 3, 4, 5, 6)) +
  labs(
    title = "Hemispheric Laterality",
    subtitle = "modified Rankin score at 90 days"
  ) +
  theme(
    plot.title = element_text(face = "bold", size = 30, lineheight = 0.1),
    plot.subtitle = element_text(size = 20, lineheight = 0.1),
    plot.caption = element_text(size = 20),
    plot.title.position = "plot",
    plot.caption.position = "plot",
    legend.title = element_blank(),
    legend.position = "right",
    legend.text = element_text(size = 15, lineheight = 0.5),
    # legend.margin = margin(r = 50),
    panel.grid.minor.x = element_blank(),
    panel.grid.major.y = element_blank(),
    axis.text.y = element_text(size = 20, lineheight = 0.5, margin = margin(r = -10)),
    axis.title.x = element_text(size = 20, lineheight = 0.5)
  )

@@

```{r}

mrsCounts <- d |>
  filter(!is.na(mrs180)) |>
  group_by(ichLaterality, mrs180) |>
  tally(name = "patients") |>
  group_by(ichLaterality) |>
  mutate(percentPatients = patients / sum(patients)) |>
  ungroup() |>
  mutate(percentPatientsLabel = percent(percentPatients, accuracy = 1))

theme_set(theme_minimal(base_size = 20, base_family = "Figtree"))

ggplot(
  data = mrsCounts,
  aes(x = ichLaterality, y = percentPatients, fill = forcats::fct_rev(mrs180))
) +
  geom_bar(stat = "identity", position = "fill", width = 0.5) +
  geom_text(aes(label = patients),
    position = position_stack(vjust = 0.5),
    color = "white",
    size = 5,
    family = "FigTree"
  ) +
  coord_flip() +
  scale_y_continuous(
    name = NULL,
    labels = scales::percent_format(accuracy = 1),
    breaks = c(seq(0, 1, 0.2))
  ) +
  scale_x_discrete(name = NULL) +
  scale_fill_manual(values = myColors, breaks = c(0, 1, 2, 3, 4, 5, 6)) +
  labs(
    title = "Hemispheric Laterality",
    subtitle = "modified Rankin score at 180 days"
  ) +
  theme(
    plot.title = element_text(face = "bold", size = 30, lineheight = 0.1),
    plot.subtitle = element_text(size = 20, lineheight = 0.1),
    plot.caption = element_text(size = 20),
    plot.title.position = "plot",
    plot.caption.position = "plot",
    legend.title = element_blank(),
    legend.position = "right",
    legend.text = element_text(size = 15, lineheight = 0.5),
    # legend.margin = margin(r = 50),
    panel.grid.minor.x = element_blank(),
    panel.grid.major.y = element_blank(),
    axis.text.y = element_text(size = 20, lineheight = 0.5, margin = margin(r = -10)),
    axis.title.x = element_text(size = 20, lineheight = 0.5)
  )

```{r}

mrsCounts <- d |>
  filter(!is.na(mrs365)) |>
  group_by(ichLaterality, mrs365) |>
  tally(name = "patients") |>
  group_by(ichLaterality) |>
  mutate(percentPatients = patients / sum(patients)) |>
  ungroup() |>
  mutate(percentPatientsLabel = percent(percentPatients, accuracy = 1))

theme_set(theme_minimal(base_size = 20, base_family = "Figtree"))

ggplot(
  data = mrsCounts,
  aes(x = ichLaterality, y = percentPatients, fill = forcats::fct_rev(mrs365))
) +
  geom_bar(stat = "identity", position = "fill", width = 0.5) +
  geom_text(aes(label = patients),
    position = position_stack(vjust = 0.5),
    color = "white",
    size = 5,
    family = "FigTree"
  ) +
  coord_flip() +
  scale_y_continuous(
    name = NULL,
    labels = scales::percent_format(accuracy = 1),
    breaks = c(seq(0, 1, 0.2))
  ) +
  scale_x_discrete(name = NULL) +
  scale_fill_manual(values = myColors, breaks = c(0, 1, 2, 3, 4, 5, 6)) +
  labs(
    title = "Hemispheric Laterality",
    subtitle = "modified Rankin score at 365 days"
  ) +
  theme(
    plot.title = element_text(face = "bold", size = 30, lineheight = 0.1),
    plot.subtitle = element_text(size = 20, lineheight = 0.1),
    plot.caption = element_text(size = 20),
    plot.title.position = "plot",
    plot.caption.position = "plot",
    legend.title = element_blank(),
    legend.position = "right",
    legend.text = element_text(size = 15, lineheight = 0.5),
    # legend.margin = margin(r = 50),
    panel.grid.minor.x = element_blank(),
    panel.grid.major.y = element_blank(),
    axis.text.y = element_text(size = 20, lineheight = 0.5, margin = margin(r = -10)),
    axis.title.x = element_text(size = 20, lineheight = 0.5)
  )

@@

@@

#
#
#
#
#
#
#
#
#
#
#
#
#
#
#
#

>>>>

---
title: "Hemispheric Lateralization in ICH"
subtitle: "Analysis"
author: "Nikhil Patel"
project:
  type: default
format:
  html:
    code-fold: true
    code-tools: true
    toc: true
    html-math-method: katex
    css: "styles.css"
---

```{r setup and data import}
#| output: false
#| echo: false

library(tidyverse)
# library(gt) # Fancy tables
library(tableone)
library(data.table)
library(haven) # Importing SAS Files
library(janitor)
library(lubridate)
library(readxl)
library(Hmisc)
library(qreport)
library(stringr)
library(qs)
library(glue)
library(scales) # Nicer labeling functions
library(ggmosaic) # Mosaic plots with ggplot
library(ggplot2)
library(ggpattern) # Pattern fills in ggplot
library(patchwork) # Combine plots nicely
library(systemfonts) ## use custom fonts (need to be installed on your OS)
library(scico) ## scico color palettes(http://www.fabiocrameri.ch/colourmaps.php) in R
library(ggtext) ## add improved text rendering to ggplot2
library(ggforce) ## add missing functionality to ggplot2
library(ggdist) ## add uncertainity visualizations to ggplot2
library(viridis)
library(dagitty)
library(rlang)
library(ggokabeito)

@@

# ggplot themes and settings
theme_set(theme_minimal(base_size = 20, base_family = "Figtree"))

@@

#### modified Rankin Scale

Overall, there does not appear to be a big difference in disability as measured by modified Rankin Scale. This is true at any of the time points used.

```{r}
#| echo: false
#| fig.width: 12
#| fig.height: 15

# mRs 90
mrsCounts <- d |>
  filter(!is.na(mrs90)) |>
  group_by(ichLaterality, mrs90) |>
  tally(name = "patients") |>
  group_by(ichLaterality) |>
  mutate(percentPatients = patients / sum(patients)) |>
  ungroup() |>
  mutate(percentPatientsLabel = percent(percentPatients, accuracy = 1))

gmrs90 <- ggplot(
  data = mrsCounts,
  aes(x = ichLaterality, y = percentPatients, fill = forcats::fct_rev(mrs90))
) +
  geom_bar(stat = "identity", position = "fill", width = 0.5) +
  geom_text(aes(label = patients),
    position = position_stack(vjust = 0.5),
    color = "white",
    size = 5,
    family = "FigTree"
  ) +
  coord_flip() +
  scale_y_continuous(
    name = NULL,
    labels = scales::percent_format(accuracy = 1),
    breaks = c(seq(0, 1, 0.2))
  ) +
  scale_x_discrete(name = NULL) +
  scale_fill_manual(values = myColors, breaks = c(0, 1, 2, 3, 4, 5, 6)) +
  labs(
    title = "90 days") +
  theme(
    plot.title = element_text(face = "bold", size = 20, lineheight = 0.1),
    plot.subtitle = element_text(size = 20, lineheight = 0.1),
    plot.caption = element_text(size = 20),
    plot.title.position = "plot",
    plot.caption.position = "plot",
    legend.title = element_blank(),
    legend.position = "right",
    legend.text = element_text(size = 15, lineheight = 0.5),
    # legend.margin = margin(r = 50),
    panel.grid.minor.x = element_blank(),
    panel.grid.major.y = element_blank(),
    axis.text.y = element_text(size = 20, lineheight = 0.5, margin = margin(r = -10)),
    axis.title.x = element_text(size = 20, lineheight = 0.5)
  )

# mRs 180
mrsCounts <- d |>
  filter(!is.na(mrs180)) |>
  group_by(ichLaterality, mrs180) |>
  tally(name = "patients") |>
  group_by(ichLaterality) |>
  mutate(percentPatients = patients / sum(patients)) |>
  ungroup() |>
  mutate(percentPatientsLabel = percent(percentPatients, accuracy = 1))

gmrs180 <- ggplot(
  data = mrsCounts,
  aes(x = ichLaterality, y = percentPatients, fill = forcats::fct_rev(mrs180))
) +
  geom_bar(stat = "identity", position = "fill", width = 0.5) +
  geom_text(aes(label = patients),
    position = position_stack(vjust = 0.5),
    color = "white",
    size = 5,
    family = "FigTree"
  ) +
  coord_flip() +
  scale_y_continuous(
    name = NULL,
    labels = scales::percent_format(accuracy = 1),
    breaks = c(seq(0, 1, 0.2))
  ) +
  scale_x_discrete(name = NULL) +
  scale_fill_manual(values = myColors, breaks = c(0, 1, 2, 3, 4, 5, 6)) +
  labs(
    title = "180 days") +
  theme(
    plot.title = element_text(face = "bold", size = 20, lineheight = 0.1),
    plot.subtitle = element_text(size = 20, lineheight = 0.1),
    plot.caption = element_text(size = 20),
    plot.title.position = "plot",
    plot.caption.position = "plot",
    legend.title = element_blank(),
    legend.position = "right",
    legend.text = element_text(size = 15, lineheight = 0.5),
    # legend.margin = margin(r = 50),
    panel.grid.minor.x = element_blank(),
    panel.grid.major.y = element_blank(),
    axis.text.y = element_text(size = 20, lineheight = 0.5, margin = margin(r = -10)),
    axis.title.x = element_text(size = 20, lineheight = 0.5)
  )

# mRs 365
mrsCounts <- d |>
  filter(!is.na(mrs365)) |>
  group_by(ichLaterality, mrs365) |>
  tally(name = "patients") |>
  group_by(ichLaterality) |>
  mutate(percentPatients = patients / sum(patients)) |>
  ungroup() |>
  mutate(percentPatientsLabel = percent(percentPatients, accuracy = 1))

gmrs365 <- ggplot(
  data = mrsCounts,
  aes(x = ichLaterality, y = percentPatients, fill = forcats::fct_rev(mrs365))
) +
  geom_bar(stat = "identity", position = "fill", width = 0.5) +
  geom_text(aes(label = patients),
    position = position_stack(vjust = 0.5),
    color = "white",
    size = 5,
    family = "FigTree"
  ) +
  coord_flip() +
  scale_y_continuous(
    name = NULL,
    labels = scales::percent_format(accuracy = 1),
    breaks = c(seq(0, 1, 0.2))
  ) +
  scale_x_discrete(name = NULL) +
  scale_fill_manual(values = myColors, breaks = c(0, 1, 2, 3, 4, 5, 6)) +
  labs(
    title = "365 days") +
  theme(
    plot.title = element_text(face = "bold", size = 20, lineheight = 0.1),
    plot.subtitle = element_text(size = 20, lineheight = 0.1),
    plot.caption = element_text(size = 20),
    plot.title.position = "plot",
    plot.caption.position = "plot",
    legend.title = element_blank(),
    legend.position = "right",
    legend.text = element_text(size = 15, lineheight = 0.5),
    panel.grid.minor.x = element_blank(),
    panel.grid.major.y = element_blank(),
    axis.text.y = element_text(size = 20, lineheight = 0.5, margin = margin(r = -10)),
    axis.title.x = element_text(size = 20, lineheight = 0.5)
  )

mrsCombined <- 
(gmrs90 + theme(plot.margin = unit(c(50,0,75,0), "pt"))) / (gmrs180 + theme(plot.margin = unit(c(0,0,75,0), "pt"))) / (gmrs365 + theme(plot.margin = unit(c(0,0,75,0), "pt"))) +
  plot_annotation(title = 'ICH Laterality and modified Rankin Scale',
                theme = theme(plot.title = element_text(face = "bold", size = 35, lineheight = 0.1))) +
  plot_layout(guides = 'collect') & theme(legend.position='right', legend.direction="vertical")

mrsCombined
```

#### Health-Related Quality of Life

Overall, there appears to be a small differences in health related quality of life, especially with mobility and self-care. This is true at any of the time points used.

```{r}
#| echo: false
#| warning: false
#| fig.width: 12
#| fig.height: 30

myColors <- c("#d76c6a", "#ae4f6e", "#7c3c6b") # https://learnui.design/tools/data-color-picker.html#palette

euroQolPlot <- function(euroSelfCare365, legendLabels, plotTitle) {
  euroQOLCounts <- d |>
  filter(!is.na({{ euroSelfCare365 }})) |>
  group_by(ichLaterality, {{ euroSelfCare365 }}) |>
  tally(name = "patients") |>
  group_by(ichLaterality) |>
  mutate(percentPatients = patients / sum(patients)) |>
  ungroup() |>
  mutate(percentPatientsLabel = percent(percentPatients, accuracy = 1))

ggplot(
  data = euroQOLCounts,
  aes(x = ichLaterality, y = percentPatients, fill = fct_rev({{ euroSelfCare365 }}))
) +
  geom_bar(stat = "identity", position = "fill", width = 0.5) +
  geom_text(aes(label = percentPatientsLabel),
    position = position_stack(vjust = 0.5),
    color = "white",
    size = 5) +
  coord_flip() +
  scale_y_continuous(
    name = NULL,
    labels = scales::percent_format(accuracy = 1),
    breaks = c(seq(0, 1, 0.2))
  ) +
  scale_x_discrete(name = NULL) +
  scale_fill_manual(values = myColors, breaks = legendLabels) +
  labs(
    title = plotTitle) +
  theme(
    plot.title = element_text(face = "bold", size = 20, lineheight = 0.1),
    plot.subtitle = element_text(size = 20, lineheight = 0.1),
    plot.caption = element_text(size = 20),
    plot.title.position = "plot",
    plot.caption.position = "plot",
    legend.title = element_blank(),
    legend.position = "bottom",
    legend.text = element_text(size = 15, lineheight = 0.5),
    panel.grid.minor.x = element_blank(),
    panel.grid.major.y = element_blank(),
    axis.text.y = element_text(size = 20, lineheight = 0.5, margin = margin(r = -10)),
    axis.title.x = element_text(size = 20, lineheight = 0.5)
  )
}
legendLabels <- c("No Problems", "Some Problems", "Confined to Bed")
ggeuroMobility90 <- euroQolPlot(euroMobility90, legendLabels, "EuroQOL Mobility")

legendLabels <- c("No Problems", "Some Problems", "Unable to Wash or Dress Myself")
ggeuroSelfCare90 <- euroQolPlot(euroSelfCare90, legendLabels, "EuroQOL Self-Care")

legendLabels <- c("No Problems", "Some Problems", "Unable to Perform My Usual Activities")
ggeuroUsual90 <- euroQolPlot(euroUsual90, legendLabels, "EuroQOL Usual Activities")

legendLabels <- c("No Pain/Discomfort", "Some Moderate Pain/Discomfort", "Extreme Pain/Discomfort")
ggeuroPain90 <- euroQolPlot(euroPain90, legendLabels, "EuroQOL Pain")

legendLabels <- c("Not Anxious/Depressed", "Moderately Anxious/Depressed", "Extremely Anxious/Depressed")
ggeuroAnxiety90 <- euroQolPlot(euroAnxiety90, legendLabels, "EuroQOL Anxiety")

legendLabels <- c("No Problems", "Some Problems", "Confined to Bed")
ggeuroMobility180 <- euroQolPlot(euroMobility180, legendLabels, "EuroQOL Mobility")

legendLabels <- c("No Problems", "Some Problems", "Unable to Wash or Dress Myself")
ggeuroSelfCare180 <- euroQolPlot(euroSelfCare180, legendLabels, "EuroQOL Self-Care")

legendLabels <- c("No Problems", "Some Problems", "Unable to Perform My Usual Activities")
ggeuroUsual180 <- euroQolPlot(euroUsual180, legendLabels, "EuroQOL Usual Activities")

legendLabels <- c("No Pain/Discomfort", "Some Moderate Pain/Discomfort", "Extreme Pain/Discomfort")
ggeuroPain180 <- euroQolPlot(euroPain180, legendLabels, "EuroQOL Pain")

legendLabels <- c("Not Anxious/Depressed", "Moderately Anxious/Depressed", "Extremely Anxious/Depressed")
ggeuroAnxiety180 <- euroQolPlot(euroAnxiety180, legendLabels, "EuroQOL Anxiety")

legendLabels <- c("No Problems", "Some Problems", "Confined to Bed")
ggeuroMobility365 <- euroQolPlot(euroMobility365, legendLabels, "EuroQOL Mobility")

legendLabels <- c("No Problems", "Some Problems", "Unable to Wash or Dress Myself")
ggeuroSelfCare365 <- euroQolPlot(euroSelfCare365, legendLabels, "EuroQOL Self-Care")

legendLabels <- c("No Problems", "Some Problems", "Unable to Perform My Usual Activities")
ggeuroUsual365 <- euroQolPlot(euroUsual365, legendLabels, "EuroQOL Usual Activities")

legendLabels <- c("No Pain/Discomfort", "Some Moderate Pain/Discomfort", "Extreme Pain/Discomfort")
ggeuroPain365 <- euroQolPlot(euroPain365, legendLabels, "EuroQOL Pain")

legendLabels <- c("Not Anxious/Depressed", "Moderately Anxious/Depressed", "Extremely Anxious/Depressed")
ggeuroAnxiety365 <- euroQolPlot(euroAnxiety365, legendLabels, "EuroQOL Anxiety")

euroQolCombined90 <- 
(ggeuroMobility90 + theme(plot.margin = unit(c(50,0,75,0), "pt"))) / (ggeuroSelfCare90 + theme(plot.margin = unit(c(0,0,75,0), "pt"))) / (ggeuroUsual90 + theme(plot.margin = unit(c(0,0,75,0), "pt"))) /
(ggeuroPain90 + theme(plot.margin = unit(c(0,0,75,0), "pt"))) / 
(ggeuroAnxiety90 + theme(plot.margin = unit(c(0,0,75,0), "pt"))) +
  plot_annotation(title = 'ICH Laterality and HRQOL at 90 days',
                theme = theme(plot.title = element_text(face = "bold", size = 35, lineheight = 0.1)))
  # plot_layout(guides = 'collect') & theme(legend.position='right', legend.direction="vertical")

euroQolCombined180 <- 
(ggeuroMobility180 + theme(plot.margin = unit(c(50,0,75,0), "pt"))) / (ggeuroSelfCare180 + theme(plot.margin = unit(c(0,0,75,0), "pt"))) / (ggeuroUsual180 + theme(plot.margin = unit(c(0,0,75,0), "pt"))) /
(ggeuroPain180 + theme(plot.margin = unit(c(0,0,75,0), "pt"))) / 
(ggeuroAnxiety180 + theme(plot.margin = unit(c(0,0,75,0), "pt"))) +
  plot_annotation(title = 'ICH Laterality and HRQOL at 180 days',
                theme = theme(plot.title = element_text(face = "bold", size = 35, lineheight = 0.1)))
  # plot_layout(guides = 'collect') & theme(legend.position='right', legend.direction="vertical")

euroQolCombined365 <- 
(ggeuroMobility365 + theme(plot.margin = unit(c(50,0,75,0), "pt"))) / (ggeuroSelfCare365 + theme(plot.margin = unit(c(0,0,75,0), "pt"))) / (ggeuroUsual365 + theme(plot.margin = unit(c(0,0,75,0), "pt"))) /
(ggeuroPain365 + theme(plot.margin = unit(c(0,0,75,0), "pt"))) / 
(ggeuroAnxiety365 + theme(plot.margin = unit(c(0,0,75,0), "pt"))) +
  plot_annotation(title = 'ICH Laterality and HRQOL at 365 days',
                theme = theme(plot.title = element_text(face = "bold", size = 35, lineheight = 0.1)))
  # plot_layout(guides = 'collect') & theme(legend.position='right', legend.direction="vertical")

euroQolCombined90
euroQolCombined180
euroQolCombined365

@@

#### Health-Related Quality of Life - Visual Analog Scale

```{r}
#| echo: false
#| warning: false
#| fig-width: 15
#| fig-height: 25

euroVASplot <- function(x, title) {
  d |>
  ggplot(aes({{x}}, fill = ichLaterality)) +
  geom_density(color = NA, alpha = 0.8) +
  labs(title = {{ title }},
        x = NULL,
        y = NULL) +
  theme(
  plot.title = element_text(face = "bold", size = 20, lineheight = 0.1),
  plot.subtitle = element_text(size = 20, lineheight = 0.1),
  plot.caption = element_text(size = 20),
  plot.title.position = "plot",
  plot.caption.position = "plot",
  legend.title = element_blank(),
  legend.position = "bottom",
  legend.text = element_text(size = 15, lineheight = 0.5),
  panel.grid.minor.x = element_blank(),
  panel.grid.major.y = element_blank(),
  axis.text.y = element_text(size = 20, lineheight = 0.5, margin = margin(r = -10)),
  axis.title.x = element_text(size = 20, lineheight = 0.5)
  )
}

ggeurovas90 <- euroVASplot(euroVAS90, "90 Days")
ggeurovas180 <- euroVASplot(euroVAS180, "180 Days")
ggeurovas365 <- euroVASplot(euroVAS365, "365 Days")

ggeuroVASCombined <- 
(ggeurovas90 + theme(plot.margin = unit(c(50,0,75,0), "pt"))) / (ggeurovas180 + theme(plot.margin = unit(c(0,0,75,0), "pt"))) / (ggeurovas365 + theme(plot.margin = unit(c(0,0,75,0), "pt"))) +
  plot_annotation(title = 'ICH Laterality EuroQOL VAS',
                theme = theme(plot.title = element_text(face = "bold", size = 35, lineheight = 0.1)))

ggeuroVASCombined

@@

```{r}
#| echo: false

dag <- dagitty('dag {
bb="0,0,1,1"
"Disease Severity" [adjusted,pos="0.152,0.791"]
"Early WLST" [adjusted,pos="0.326,0.215"]
"Functional Outcome" [outcome,pos="0.916,0.455"]
"ICH Laterality" [exposure,pos="0.070,0.455"]
Age [adjusted,pos="0.153,0.958"]
Comorbidities [adjusted,pos="0.380,0.950"]
Neurosurgery [adjusted,pos="0.736,0.148"]
Rehabilitation [latent,pos="0.849,0.703"]
"Disease Severity" -> "Early WLST"
"Disease Severity" -> "Functional Outcome"
"Disease Severity" -> Neurosurgery
"Disease Severity" -> Rehabilitation
"Early WLST" -> "Functional Outcome"
"ICH Laterality" -> "Early WLST"
"ICH Laterality" -> "Functional Outcome"
"ICH Laterality" -> Neurosurgery
Age -> "Functional Outcome"
Age -> Neurosurgery
Age -> Rehabilitation
Age -> Comorbidities
Comorbidities -> "Functional Outcome"
Comorbidities -> Neurosurgery
Comorbidities -> Rehabilitation
Comorbidities -> "Disease Severity"
Neurosurgery -> "Functional Outcome"
Rehabilitation -> "Functional Outcome"
}')

plot(dag)
```

**Add Deaths to ATACH data!**

@@
